DPIV Analysis and Real Time Implementation

### 2022-12-02 Paper/main.tex
filling the paper
Modifying main.tex
change introduction
new image inserted
Introduction of subsection

\bibliographystyle{IEEEtran}
% DO NOT ERASE THE NEXT LINE,
% ONLY COMMENT IT AND DECOMMENT THE NEXT-NEXT, IF YOU NEED
\bibliography{./bibCustom}

>>>>

\section{Introduction}

This paper ecc...

\section{Materials and Methods}

\subsection{System Design and Hardware Platform Realization}\label{sec:design}

From a methodological point of view, the experimental characterization of the process takes place through the acquisition of video signals that allow studying different interaction mechanisms between particles/cells subject to external hydrodynamic actuation.
The captured videos is then analyzed using the Digital Particle Image Velocimetry (DPIV).
\\From a hardware realization point of view, the focus is put on interfacing the microfluidic device with a video signal acquisition system.
Then different sources of actuation, mechanical by syringe pumps and optical by LED light are considered through which it is possible to study different interaction mechanisms between micro-particles subjected to different external stresses, in particular to sinusoidal flows with frequency and amplitude values to be fixed.

%$\flowrate$, $\flowratewatercommand$,$\channelArea$ are all examples of variables defined in "symbol-definition.tex"

\subsection{DPIV Online Platform Implementation}\label{sec:method}

\section{Experiments}

\subsection{Experimental Setup}

\subsection{Experimental Results}

\subsubsection{Offline vs Online}

\subsubsection{Micro-Particles counting and velocity}

\paragraph{Particles suspended in fluids with different densities}

\paragraph{Viable cells, Dead cells and Synthetic Particles in comparison}

\section{Conclusions}

%\bibliographystyle{IEEEtran}
% DO NOT ERASE THE NEXT LINE,
% ONLY COMMENT IT AND DECOMMENT THE NEXT-NEXT, IF YOU NEED
%\bibliography{./bibCustom}
